---
title: "431 Class 09"
author: Thomas E. Love, Ph.D.
date: "2025-09-30"
format:
  revealjs: 
    theme: dracula
    self-contained: true
    slide-number: true
    footnotes-hover: true
    preview-links: auto
    date-format: iso
    logo: 431-2025-logo-full.png
    footer: "431 Class 09 | 2025-09-30 | <https://thomaselove.github.io/431-2025/>"
---

## Today's Agenda

- New Data, with Missing Values
  - Using `naniar` to help identify missingness
- More on One-Factor Analysis of Variance (ANOVA)
  - Pairwise comparisons of means
    - Getting actual simultaneous confidence intervals
    - Bonferroni and Tukey HSD procedures
  - Considering an Outcome Transformation
- Favorite Movies: Session 2

## Load packages and set theme

```{r}
#| echo: true
#| message: false

library(janitor)
library(DescTools)  ## NEW - for Bonferroni and Tukey HSD CIs
library(naniar)     ## dealing with missing data
library(car)        ## for the Box-Cox plot     
library(patchwork)
library(rstanarm)
library(easystats)
library(tidyverse)

theme_set(theme_lucid()) ## new theme for ggplots!
knitr::opts_chunk$set(comment = NA)

source("c09/data/Love-431.R") # for the lovedist() function
```

- See [Class 09 README](https://github.com/THOMASELOVE/431-classes-2025/blob/main/class09/README.md) for alternative ggplot themes.

## Get the data

[EUROFAMCARE project](https://www.uke.de/extern/eurofamcare/): a survey on the situation of family carers of older people in Europe.

```{r}
#| echo: true
ecare_orig <- read_csv("c09/data/eurocare.csv", show_col_types = FALSE) |>
  janitor::clean_names() |>
  mutate(across(where(is.character), as_factor)) |>
  mutate(subject = as.character(subject))

dim(ecare_orig)
names(ecare_orig)
```

## Missingness?

```{r}
#| echo: true

miss_var_summary(ecare_orig)
```

## Today's Variables

```{r}
#| echo: true
ecare_new <- ecare_orig |>
  dplyr::select(subject, hours, c_education, pos_impact, dependency)

data_codebook(ecare_new |> select(!subject))
```

## Put factors in sensible orders?

```{r}
#| echo: true

ecare_new <- ecare_new |>
  mutate(c_education = fct_relevel(c_education, "High", 
                                   "Middle", "Low"),
         dependency = fct_relevel(dependency, "independent", "slight",
                                  "moderate", "severe"))

ecare_new |> tabyl(c_education, dependency)
```

## Do mean `hours` vary by `c_education`?

```{r}
#| echo: true

ggplot(ecare_new, aes(y = hours, x = c_education)) +
  geom_violin(aes(fill = c_education)) + 
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, size = 3, col = "red") +
  scale_fill_viridis_d(alpha = 0.3) +
  guides(fill = "none")
```

## Try again with complete cases?

```{r}
#| echo: true

ecare_1 <- ecare_new |> 
  filter(complete.cases(hours, c_education))
dim(ecare_1)
```

```{r}
#| echo: true
#| output-location: slide

ggplot(ecare_1, aes(y = hours, x = c_education)) +
  geom_violin(aes(fill = c_education)) + 
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, size = 3, col = "red") +
  scale_fill_viridis_d(alpha = 0.3) +
  guides(fill = "none")
```

## Do `hours` vary by `c_education`? (1/2)

```{r}
#| echo: true

ecare_1 |> group_by(c_education) |> reframe(lovedist(hours))
```

- Sample mean `hours` are somewhat smaller for carers with higher levels of education. 
  - Does these mean differences seem meaningful?
  - Does each group's data follow a Normal distribution?

## Do `hours` vary by `c_education`? (2/2)

```{r}
#| echo: true

ecare_1 |> group_by(c_education) |> reframe(lovedist(hours))
```

- What else might we consider here?
  - Do we have a balanced design?
  - Are sample variances very different from each other?

## ANOVA model for this comparison

```{r}
#| echo: true

m1 <- lm(hours ~ c_education, data = ecare_1)
anova(m1)
model_parameters(m1, ci = 0.95)
```

## Holm 95% pairwise comparisons??

```{r}
#| echo: true

estimate_contrasts(m1, ci = 0.95, p_adjust = "holm")
```

- **NEW**: CIs aren't actually changed from `model_parameters()`, just the `p` values!
- Holm procedure stops once it finds a small *p* value. 

## Bonferroni approach?

```{r}
#| echo: true

estimate_contrasts(m1, ci = 0.95, p_adjust = "bonferroni")
```

- Again, only the *p* values change here... what to do?

## Actual Bonferroni 95% CIs?

```{r}
#| echo: true
## this requires library(DescTools)

PostHocTest(aov(m1), method = "bonferroni", 
            conf.level = 0.95, ordered = FALSE)
```

## Plot means with Bonferroni CIs

```{r}
#| echo: true

par(mar=c(3,10,3,3), las = 1)
plot(PostHocTest(aov(m1), method = "bonferroni", conf.level = 0.95))
```

## What about Tukey HSD intervals?

Tukey’s HSD approach is a better choice than Holm for **pre-planned comparisons** with a **balanced (or nearly balanced)** design. Which should we use here?

```{r}
#| echo: true

PostHocTest(aov(m1), method = "hsd", conf.level = 0.95, ordered = TRUE)
```

## Plot means with Tukey CIs

```{r}
#| echo: true

par(mar=c(3,10,3,3), las = 1)
plot(PostHocTest(aov(m1), method = "hsd", conf.level = 0.95))
```


## Does model `m1` work well?

```{r}
#| echo: true

plot(m1, which = 2)
```

## Could we transform the outcome?

```{r}
#| echo: true

boxCox(m1)
```

## Impact of log transformation

```{r}
#| echo: true

ecare_1 |> group_by(c_education) |> reframe(lovedist(log(hours)))
```

```{r}
#| echo: true
#| output-location: slide

ggplot(ecare_1, aes(y = log(hours), x = c_education)) +
  geom_violin(aes(fill = c_education)) + 
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, size = 3, col = "red") +
  scale_fill_viridis_d(alpha = 0.3) +
  guides(fill = "none")
```

## ANOVA after Transforming `hours`

```{r}
#| echo: true

m2 <- lm(log(hours) ~ c_education, data = ecare_1)

anova(m2)
```

- What's the conclusion here?

## Bonferroni 95% CIs for log(hours)

```{r}
#| echo: true

PostHocTest(aov(m2), method = "bonferroni", 
            conf.level = 0.95, ordered = TRUE)
```

- Variable predicted is actually **log(hours)**

## Bonferroni 95% CIs for log(hours)

```{r}
#| echo: true

par(mar=c(3,10,3,3), las = 1)
plot(PostHocTest(aov(m2), method = "bonferroni", 
            conf.level = 0.95, ordered = TRUE))
```

## Normality still a problem?

```{r}
#| echo: true

plot(m2, which = 2)
```

## Kruskal-Wallis ANOVA

If the data were severely skewed, you might try:

```{r}
#| echo: true

kruskal.test(hours ~ c_education, data = ecare_1)
```

- $H_0$: The four education groups have the same center to their `hours` distributions.
- $H_A$: At least one group has a shifted distribution, with a different center to its `hours`.

## K Samples: Comparing Means I

1. What is the outcome under study?
2. What are the ($K \geq 2$) treatment/exposure groups?
3. Were the data in fact collected using independent samples?
4. Are the data random samples from the population(s) of interest? Or is there at least a reasonable argument for generalizing from the samples to the population(s)?
5. What confidence level do we require?

## K Samples: Comparing Means II

6. Are we doing one-sided or two-sided testing? (usually 2-sided)
7. What does the distribution of each individual sample tell us about which inferential procedure to use?
8. Are there meaningful differences between population means?
9. Can we identify pairwise comparisons of means that show meaningful differences using an appropriate procedure that protects against Type I error expansion due to multiple comparisons?

## Another ANOVA Example

- Starting on the next slide, there is a second one-factor ANOVA example (using the same EUROFAMCARE data) for self-study.
- I have edited [Section 9.9 of the Course Book](https://thomaselove.github.io/431-book/09_transmore.html#pairwise-comparisons-of-means) to reflect correct simultaneous CIs for the Bonferroni and Tukey methods as presented today.

OK, let's return to discussing the [favorite movies](https://github.com/THOMASELOVE/431-classes-2025/tree/main/class09) data.


# A Second One-Factor ANOVA Example for Self-Study

## Same data, new question

Do `pos_impact` means differ by `dependency` level?

```{r}
#| echo: true

ecare_2 <- ecare_new |> filter(complete.cases(pos_impact, dependency))

ecare_2 |> group_by(dependency) |> reframe(lovedist(pos_impact))
```

- Balanced design?
- Reasonable to pool standard deviations?

## Draw comparison boxplots

- Do we see serious problems with Normality?

```{r}
#| echo: true
#| output-location: slide

ggplot(ecare_2, aes(y = pos_impact, x = dependency)) +
  geom_violin(aes(fill = dependency)) + 
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, size = 3, col = "red") +
  scale_fill_viridis_d(alpha = 0.3) +
  guides(fill = "none") +
  coord_flip()
```

## Fit an ANOVA model

```{r}
#| echo: true

m3 <- lm(pos_impact ~ dependency, data = ecare_2)
anova(m3)
model_parameters(m3, ci = 0.95)
```

## Simultaneous Bonferroni CIs?

```{r}
#| echo: true

PostHocTest(aov(m3), method = "bonferroni", conf.level = 0.95)
```

## Plot means with Bonferroni CIs

```{r}
par(mar=c(3,10,3,3), las = 1)
plot(PostHocTest(aov(m3), 
                 method = "bonferroni", conf.level = 0.95))
```


## Consider transforming `pos_impact`?

```{r}
#| echo: true

boxCox(m3)
```

## Impact of square transformation

```{r}
#| echo: true

ecare_2 |> group_by(dependency) |> reframe(lovedist((pos_impact^2)))
```

```{r}
#| echo: true
#| output-location: slide

ggplot(ecare_2, aes(y = (pos_impact^2), x = dependency)) +
  geom_violin(aes(fill = dependency)) + 
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, size = 3, col = "red") +
  scale_fill_viridis_d(alpha = 0.3) +
  guides(fill = "none") + 
  coord_flip()
```

## ANOVA after Transformation

```{r}
#| echo: true

m4 <- lm((pos_impact^2) ~ dependency, data = ecare_2)
anova(m4)
model_parameters(m4, ci = 0.95)
```

## Simultaneous Bonferroni CIs?

```{r}
#| echo: true

PostHocTest(aov(m4), method = "bonferroni", conf.level = 0.95)
```

## Bonferroni 95% CIs: (`pos_impact`^2)

```{r}
#| echo: true

par(mar=c(3,10,3,3), las = 1)
plot(PostHocTest(aov(m4), method = "bonferroni", 
            conf.level = 0.95, ordered = TRUE))
```

## Session Information

```{r}
#| echo: true

xfun::session_info()
```