---
title: "431 Class 22"
author: Thomas E. Love, Ph.D.
date: "2025-11-18"
format:
  revealjs: 
    theme: dracula
    self-contained: true
    slide-number: true
    footnotes-hover: true
    embed-resources: true
    preview-links: auto
    date-format: iso
    logo: 431-2025-logo-full.png
    footer: "431 Class 22 | 2025-11-18 | <https://thomaselove.github.io/431-2025/>"
---

## Today's Packages

- Today's (arbitrary) confidence level = **93%**.

```{r}
#| echo: true
#| message: false

library(naniar)
library(janitor)
library(mice)
library(car)
library(patchwork)
library(broom)
library(GGally)
library(gt); library(gtExtras)
library(glue)
library(nhanesA)     ## ingest NHANES data
library(olsrr)       ## for best subsets
library(easystats)
library(tidyverse)

theme_set(theme_light())
```

## Today's Agenda

- An example from NHANES 2013-2014
- Dealing with Missing Data, Partitioning, etc.
- Most of the things we've done previously, plus...
- Automated Variable Selection in Multiple Regression
  - Stepwise regression (AIC-based backwards elimination)
  - Best subsets (based on Mallows' $C_p$)
- Some rudimentary cross-validation approaches

## Outcome and Potential Predictors

Data Source: [NHANES 2013-2014](https://wwwn.cdc.gov/nchs/nhanes/continuousnhanes/default.aspx?BeginYear=2013)

Today, we will try to predict `waist` circumference (in cm) using some combination of these 12 candidate predictors:

- body weight (in kg): expected to be primary driver
- demographics: age, sex, race/ethnicity, marital status, educational attainment, and insurance status
- systolic and diastolic blood pressure (1st reading), total cholesterol, self-rated oral health, sedentary minutes/day

## NHANES 2013-14 data we'll use

- We'll use the [Demographics file](https://wwwn.cdc.gov/nchs/nhanes/search/datapage.aspx?Component=Demographics&Cycle=2013-2014): `DEMO_H`
- from the [Examination data](https://wwwn.cdc.gov/nchs/nhanes/search/datapage.aspx?Component=Examination&CycleBeginYear=2013): Blood Pressure `BPX_H`, and Body Measures `BMX_H`
- from the [Laboratory data](https://wwwn.cdc.gov/nchs/nhanes/search/datapage.aspx?Component=Laboratory&Cycle=2013-2014): Cholesterol - Total `TCHOL_H` 
- and from the [Questionnaire data](https://wwwn.cdc.gov/nchs/nhanes/search/datapage.aspx?Component=Questionnaire&Cycle=2013-2014): Health Insurance `HIQ`, Oral Health `OHQ`, and Physical Activity `PAQ`

## Data Ingest from NHANES 2013-14

- In the next 2 slides, I'll show the work I did to create a raw data set containing data on subjects from this administration of NHANES, using the `nhanesA` package, but I won't execute that code. 

Instead, I placed an R data set of the raw data (**nh_H_raw.Rds**) on [our 431-data page](https://github.com/THOMASELOVE/431-data), which we'll use shortly.

- Source: [NHANES 2013-2014 Data](https://wwwn.cdc.gov/nchs/nhanes/continuousnhanes/default.aspx?BeginYear=2013)


## R code ingesting NHANES data

```{r}
#| echo: true
#| eval: false
demoH <- nhanes('DEMO_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
bpxH <- nhanes('BPX_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
bmxH <- nhanes('BMX_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
tcholH <- nhanes('TCHOL_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
hiqH <- nhanes('HIQ_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
ohqH <- nhanes('OHQ_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
paqH <- nhanes('PAQ_H', translated = FALSE) |> 
  tibble() |> mutate(SEQN = as.character(SEQN))
```

## R code aggregating NHANES data

```{r}
#| echo: true
#| eval: false
t12 <- left_join(demoH, bpxH, by = "SEQN")
t123 <- left_join(t12, bmxH, by = "SEQN")
t1234 <- left_join(t123, tcholH, by = "SEQN")
t12345 <- left_join(t1234, hiqH, by = "SEQN")
t123456 <- left_join(t12345, ohqH, by = "SEQN")
nh_H_raw <- left_join(t123456, paqH, by = "SEQN")

write_rds(nh_H_raw, "c22/data/nh_H_raw.Rds")
```

## Using the `.Rds` file: pruning rows

Let's ingest the raw data from the `Rds` file. 

```{r}
#| echo: true

nh_H_raw <- read_rds("c22/data/nh_H_raw.Rds")
dim(nh_H_raw)
```

Then we want to focus on adults ages 21-79 (Age is in the `RIDAGEYR` variable) who were both interviewed and MEC examined (`RIDSTATR = 2`)

```{r}
#| echo: true
nh_H <- nh_H_raw |> 
  filter(RIDSTATR == 2,
         RIDAGEYR >= 21 & RIDAGEYR <= 79)
dim(nh_H)
```

## Pruning the Variables

... and replacing **Refused**, and **Don't Know** codes with `NA`.

```{r}
#| echo: true

nh_H <- nh_H |>
  select(SEQN, RIAGENDR, RIDAGEYR, RIDRETH3, DMDEDUC2, DMDMARTL,
         BPXSY1, BPXDI1, BMXWT, BMXWAIST, LBXTC, 
         HIQ011, HIQ031A, HIQ031B, HIQ031D, 
         OHQ845, PAD680, WTINT2YR, WTMEC2YR) |>
  replace_with_na(replace = 
         list(DMDEDUC2 = c(7, 9), DMDMARTL = c(77, 99), HIQ011 = c(7, 9), 
              HIQ031A = c(77, 99), OHQ845 = c(7, 9), PAD680 = c(7777, 9999)))
```

## Factor Cleaning (1/2)

```{r}
#| echo: true
nh_H <- nh_H |> 
  mutate(sex = fct_recode(factor(RIAGENDR), "M" = "1", "F" = "2")) |>
  mutate(race_eth = fct_recode(factor(RIDRETH3), 
            "Hispanic" = "1", "Hispanic" = "2", "NH_White" = "3", 
            "NH_Black" = "4", "NH_Asian" = "6", "Other" = "7")) |>
  mutate(educ = fct_recode(factor(DMDEDUC2),
            "NonHSGrad" = "1", "NonHSGrad" = "2", "HSGrad" = "3",
            "SomeCollege" = "4", "CollegeGrad" = "5")) |>
  mutate(marital = fct_recode(factor(DMDMARTL),
            "Together" = "1", "Formerly" = "2", "Formerly" = "3", 
            "Formerly" = "4", "Never" = "5", "Together" = "6"))
```

## Factor Cleaning (2/2)

```{r}
#| echo: true
nh_H <- nh_H |> 
  mutate(insur = factor(case_when(
    HIQ011 == 2 ~ "Uninsured",
    HIQ011 == 1 & HIQ031D == 17 ~ "Medicaid",
    HIQ011 == 1 & HIQ031B == 15 ~ "Medicare",
    HIQ011 == 1 & HIQ031A == 14 ~ "Commercial"))) |>
  mutate(insur = fct_relevel(insur, "Medicare")) |>
  mutate(oral_h = fct_recode(factor(OHQ845),
            "E" = "1", "VG" = "2", "G" = "3", "F" = "4", "P" = "5"))
```

#### Variable Renaming

```{r}
#| echo: true
nh_H <- nh_H |> 
  rename(age = RIDAGEYR, sbp1 = BPXSY1, dbp1 = BPXDI1, 
         wt_kg = BMXWT, waist = BMXWAIST, tot_chol = LBXTC, 
         sedentary = PAD680)
```

## Changing implausible values to NA

- We're going to treat as missing values of systolic and diastolic blood pressure and total cholesterol that we think are implausible^[In part, this is so you can see how to do it.].
- Suppose we believe `sbp1` and `tot_chol` should be at least 70, while `dbp1` should be at least 40.

```{r}
#| echo: true

nh_H <- nh_H |> 
  replace_with_na_at(.vars = c("sbp1", "tot_chol"), condition = ~ .x < 70) |>
  replace_with_na_at(.vars = "dbp1", condition = ~ .x < 40)
```

## The `nh_H` data after that work

```{r}
#| echo: true
nh_H <- nh_H |> 
  select(SEQN, waist, wt_kg, age, sex, race_eth, marital, educ, insur, 
         sbp1, dbp1, waist, tot_chol, oral_h, sedentary, WTINT2YR, WTMEC2YR)

gt_preview(nh_H)
```

## Variable Descriptions (1/3)

Variable | Description | NA
-------: | :-------------------------------- | --:
`SEQN` | Subject identifier code | `r n_miss(nh_H$SEQN)`
`waist` | Waist circumference (cm) | `r n_miss(nh_H$waist)`
`wt_kg` | Body weight (kg) | `r n_miss(nh_H$wt_kg)`
`age` | age in years (21-79) | `r n_miss(nh_H$age)`
`sex` | M or F | `r n_miss(nh_H$sex)`
`race_eth` | race/ethnicity (5 categories) | `r n_miss(nh_H$race_eth)`

## Variable Descriptions (2/3)

Variable | Description | NA
-------: | :-------------------------------- | --:
`marital` | marital status (3 categories) | `r n_miss(nh_H$marital)`
`educ` | educational attainment (4 categories) | `r n_miss(nh_H$educ)`
`insur` | primary insurance (4 categories) | `r n_miss(nh_H$insur)`
`sbp1` | 1st Systolic BP reading (mm Hg) | `r n_miss(nh_H$sbp1)`
`dbp1` | 1st Diastolic BP reading (mm Hg) | `r n_miss(nh_H$dbp1)`
`tot_chol` | Total Cholesterol (mg/dl) | `r n_miss(nh_H$tot_chol)`

## Variable Descriptions (3/3)

Variable | Description | NA
-------: | :-------------------------------- | --:
`oral_h` | self-reported oral health (5 levels) | `r n_miss(nh_H$oral_h)`
`sedentary` | typical day: sedentary activity (minutes) | `r n_miss(nh_H$sedentary)`
`WTINT2YR` | sampling weight for interview items | `r n_miss(nh_H$WTINT2YR)`
`WTMEC2YR` | sampling weight for examination items | `r n_miss(nh_H$WTMEC2YR)`

## `data_codebook()` results

```{r}
#| echo: true
data_codebook(nh_H |> select(-SEQN, -WTINT2YR, -WTMEC2YR))
```

## Missing Data by Variable

```{r}
#| echo: true
miss_var_summary(nh_H) |> filter(n_miss > 0)
```

## Missing Data

```{r}
#| echo: true

dim(nh_H)
miss_case_table(nh_H)
pct_miss_case(nh_H)
```

## Missingness Mechanism

Can we assume the data are MCAR, per Little's test?

```{r}
#| echo: true
mcar_test(nh_H)
```

- Looks like we'll need to assume MAR and do some imputation.

## Outcome and Potential Predictors

Again, our goal is to try to predict `waist` circumference (in cm) using some combination of these 12 candidate predictors:

- body weight (in kg): expected to be primary driver
- demographics: age, sex, race/ethnicity, marital status, educational attainment, and insurance status
- systolic and diastolic blood pressure, total cholesterol, self-rated oral health, sedentary minutes/day

We'll generate several possible models.

## Single imputation

```{r}
#| label: single_imputation
#| echo: true
#| warning: true

set.seed(20251118)
nh_i1 <- mice(nh_H, m = 1, printFlag = FALSE)
nh_si <- complete(nh_i1) ## si for single imputation
n_miss(nh_si)
```

We'll use this single imputation for decision-making...

## Looking at the logged events

- The main reasons we get logged events are:
  - We have a "constant" term (or a variable of type **character**, which is removed from the imputation model, or
  - One variable is completely collinear with another.

```{r}
#| echo: true

nh_i1$loggedEvents
```


## Partition the Data

```{r}
#| label: partition_data
#| echo: true
c(nrow(nh_si), n_distinct(nh_si$SEQN)) # check that SEQNs are all distinct

set.seed(2025431)

nh_train <- nh_si |> slice_sample(n = 4000, replace = FALSE)
nh_test <- anti_join(nh_si, nh_train, by = "SEQN")

c(nrow(nh_train), nrow(nh_test))
```

## Waist Circumference (our outcome)

```{r}
bw = 2.5 # specify width of bins in histogram

p1 <- ggplot(nh_train, aes(x = waist)) +
  geom_histogram(binwidth = bw, fill = "black", col = "white") +
  stat_function(fun = function(x)
    dnorm(x, mean = mean(nh_train$waist, na.rm = TRUE),
          sd = sd(nh_train$waist, na.rm = TRUE)) *
      length(nh_train$waist) * bw,  
    geom = "area", alpha = 0.5, fill = "lightblue", col = "blue") +
  labs(x = "Waist Circumference (cm)", y = "",
       title = "Histogram & Normal Curve") 

p2 <- ggplot(nh_train, aes(sample = waist)) +
  geom_qq() + geom_qq_line(col = "red") +
  labs(y = "Waist Circumference (cm)",
       x = "Standard Normal Distribution",
       title = "Normal Q-Q plot")

p3 <- ggplot(nh_train, aes(x = waist, y = "")) +
  geom_violin(fill = "cornsilk") +
  geom_boxplot(width = 0.2) +
  stat_summary(fun = mean, geom = "point", 
               shape = 16, col = "red") +
  labs(y = "", x = "Waist Circumference (cm)",
    title = "Boxplot with Violin")

p1 + (p2 / p3 + plot_layout(heights = c(2, 1))) +
  plot_annotation(
    title = "Waist Circumference seems a little right skewed",
    subtitle = glue("NHANES 2013-14 Training Data Set (n = ", nrow(nh_train), ")"))
```

## Transform our Outcome?

```{r}
#| echo: true
t_check <- lm(waist ~ wt_kg + age + sex + race_eth + marital + educ + 
                insur + sbp1 + dbp1 + tot_chol + oral_h + sedentary,
              data = nh_train)
boxCox(t_check)
```

## Collinearity?

```{r}
#| echo: true

check_collinearity(t_check)
```

# Automated Predictor Selection (not usually a great idea, but ...)

## Stepwise Regression Process

Start with a model including all candidate predictors.

- R looks at each variable in turn to see what would happen to AIC if we dropped it from the model.
- It then drops the variable that most reduces the AIC, creating the first step down.
- Then it repeats the process with the new stepped down model and drops the variable that most reduces the AIC now.
- When we can no longer drop a variable and reduce AIC, stop.

## Stepwise Regression

Start with a 12-predictor model, predicting `waist` circumference.

```{r}
#| echo: true
fit_all12 <- lm(waist ~ wt_kg + age + sex + race_eth + 
                  marital + educ + insur + sbp1 + dbp1 + 
                  tot_chol + oral_h + sedentary, 
                data = nh_train)
```

Here's one way to run a backwards stepwise elimination search of our regression model, using AIC as the measure to tell us when to stop removing variables.

```{r}
#| echo: true
#| output-location: slide
step_res <- step(fit_all12, direction = "backward")
```

Results on the next slide.

## So What Happened?

- The big model (12 predictors) had an AIC of 13887
- Dropping `dbp1` reduced the AIC a little
- Then dropping `sbp1` reduced the AIC to 13886
- but at that point, no additional variable removals reduce AIC. The best we can do is to drop `sedentary` but that increases AIC back to 13887.

## Stepwise Regression Result

So we drop two of the 12 predictors (`sbp1` and `dbp1`) and keep the remaining ten (`wt_kg`, `age`, `sex`, `race_eth`, `marital`, `educ`, `insur`, `tot_chol`, `oral_h` and `sedentary`).

```{r}
#| echo: true
fit_step10 <- lm(waist ~ wt_kg + age + sex + race_eth + marital +
                   educ + insur + tot_chol + oral_h + sedentary,
                 data = nh_train)
```

It turns out that stepwise regression is pretty bad, even by the standards of automated variable selection procedures. Are there better options?

- Can we generate other competitive candidate predictor sets?

## A Best Subsets Approach

Again, we start with our big model `fit_all12`, with all 12 predictors, but now we use a function from the **olsrr** package to complete some automated variable selection^[*Caution*: this process takes a while.]. 

```{r}
#| label: best-subsets
#| echo: true

nh_best_res <- 
  ols_step_best_subset(fit_all12, max_order = 8, metric = "cp")
```

This code identifies the best subsets of variables according to Mallows' $C_p$ statistic, while restricting the search to models with 1-8 variables (of our original 12) included. Results on the next slide...

## Results from "Best Subsets" Search {.smaller}

```{r}
nh_best_res
```

## We'll compare four options

I've somewhat arbitrarily selected^[`fit12` is the "kitchen sink", `fit10` is "stepwise", `fit04` has a nice adjusted $R^2$, and `fit01` is the most crucial predictor.] these four options.

```{r}
#| echo: true
fit_12 <- lm(waist ~ wt_kg + age + sex + race_eth + marital + 
               educ + insur + sbp1 + dbp1 + tot_chol + 
               oral_h + sedentary,
             data = nh_train)

fit_10 <- lm(waist ~ wt_kg + age + sex + race_eth + marital + 
               educ + insur + tot_chol + oral_h + sedentary,
             data = nh_train)

fit_04 <- lm(waist ~ wt_kg + age + sex + race_eth, data = nh_train)

fit_01 <- lm(waist ~ wt_kg, data = nh_train)
```

## Two Model Checks (`fit_12`)

```{r}
#| label: pp-check12
#| echo: true
set.seed(43101); check_model(fit_12, detrend = FALSE, check = c("pp_check", "linearity"))
```

## Two Model Checks (`fit_10`)

```{r}
#| label: pp-check10
#| echo: true
set.seed(43102); check_model(fit_10, detrend = FALSE, check = c("pp_check", "linearity"))
```

## Two Model Checks (`fit_04`)

```{r}
#| label: pp-check04
#| echo: true
set.seed(43103); check_model(fit_04, detrend = FALSE, check = c("pp_check", "linearity"))
```

## Two Model Checks (`fit_01`)

```{r}
#| label: pp-check01
#| echo: true
set.seed(43104); check_model(fit_01, detrend = FALSE, check = c("pp_check", "linearity"))
```

## Other Checks for Model `fit_04`

```{r}
#| label: check-model04_2
#| echo: true
set.seed(43105); check_model(fit_04, detrend = FALSE, check = c("homogeneity", "outliers"))
```

## Still more Checks for Model `fit_04`

```{r}
#| label: check-model04_3
#| echo: true
set.seed(43106); check_model(fit_04, detrend = FALSE, check = c("vif", "qq"))
```

## Training Sample Performance

```{r}
#| label: plot-compare-performance
#| echo: true
plot(compare_performance(fit_12, fit_10, fit_04, fit_01))
```

## Training Sample Performance

```{r}
#| label: compare-performance-ranks
#| echo: true
compare_performance(fit_12, fit_10, fit_04, fit_01, rank = TRUE) |> 
  gt() |> fmt_number(decimals = 3) |> gt_theme_espn()
```

## Cross-Validation Performance

In the training sample, we'll try some cross-validation.

```{r}
#| label: cross-validation
#| echo: true
set.seed(20254312)
performance_accuracy(fit_12, method = "cv", k = 5)
performance_cv(fit_12)
```

This is something we'll do in 432, too. We can do the same thing for the other three models (R code on next slide.)

## R code for other models

```{r}
#| echo: true
#| eval: false
set.seed(20254313)
performance_accuracy(fit_10, method = "cv", k = 5)
performance_cv(fit_10)

set.seed(20254314)
performance_accuracy(fit_04, method = "cv", k = 5)
performance_cv(fit_04)

set.seed(20254315)
performance_accuracy(fit_01, method = "cv", k = 5)
performance_cv(fit_01)
```

## Cross-Validation Results

- across the four models we're considering...

Model | Accuracy | $MSE_{30}$ | $RMSE_{30}$ | $R^2_{30}$
-----: | --------: | ------: | ------: | ------: 
`fit_12` | 0.9409 | 34 | 5.8 | 0.87
`fit_10` | 0.9412 | 34 | 5.8 | 0.88
`fit_04` | 0.9378 | 35 | 5.9 | 0.87
`fit_01` | 0.9047 | 51 | 7.1 | 0.82

- Accuracy = correlation of `waist`$_{observed}$, `waist`$_{predicted}$.
- Other summaries use 30% holdout approach.

## Predicting into Test Sample

```{r}
#| label: augment-newdata
#| echo: true
aug01_test <- augment(fit_01, newdata = nh_test) |> mutate(mod = "fit_01")
aug04_test <- augment(fit_04, newdata = nh_test) |> mutate(mod = "fit_04")
aug10_test <- augment(fit_10, newdata = nh_test) |> mutate(mod = "fit_10")
aug12_test <- augment(fit_12, newdata = nh_test) |> mutate(mod = "fit_12")

temp14 <- bind_rows(aug01_test, aug04_test)
temp140 <- bind_rows(temp14, aug10_test)
test_res <- bind_rows(temp140, aug12_test) |>
  relocate(SEQN, mod, waist, everything()) |> arrange(SEQN, mod)
```

## Four Summary Measures

```{r}
#| label: calculate_summaries_test
#| echo: true

test_summary <- test_res |> 
  group_by(mod) |>
  summarize(MAPE = mean(abs(.resid)),
            Max_APE = max(abs(.resid)),
            RMSE = sqrt(mean(.resid^2)),
            R2_val = cor(waist, .fitted)^2)

test_summary |> gt() |> fmt_number(decimals = 4) |> 
  gt_theme_espn()
```

# Multiple Imputation

## We'd like to do 25 imputations

25 imputations on model `fit_04` takes a little while (60 seconds on my machine.)

```{r}
#| label: run_25_multiple_imps
#| echo: true
pct_miss_case(nh_H)

imp25_ests <- nh_H |>
  mice(m = 25, seed = 4312345, print = FALSE) |>
  with(lm(waist ~ wt_kg + age + sex + race_eth)) |>
  pool()
```

## Pooled Results for model `fit_04`

```{r}
#| echo: true
glance(imp25_ests)

tidy(imp25_ests, conf.int = TRUE, conf.level = 0.93) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  gt() |> fmt_number(decimals = 3, columns = c(-p.value)) 
```

## Training Sample Results for `fit_04`

```{r}
#| echo: true
glance(fit_04) |> select(nobs, r.squared, adj.r.squared)

tidy(fit_04, conf.int = TRUE, conf.level = 0.93) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  gt() |> fmt_number(decimals = 3) |> gt_theme_guardian()
```

## Single Imputation Results for `fit_04`

Our model `fit_04` uses `wt_kg`, `age`, `sex` and `race_eth` to predict `waist`. Our identifying code is in `SEQN`.

```{r}
#| echo: true

fit4_si <- lm(waist ~ wt_kg + age + sex + race_eth, data = nh_si)

n_obs(fit4_si)
```

## Single Imputation Results for `fit_04`

```{r}
#| echo: true
glance(fit4_si) |> select(nobs, r.squared, adj.r.squared)

tidy(fit4_si, conf.int = TRUE, conf.level = 0.93) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  gt() |> fmt_number(decimals = 3) |> gt_theme_guardian()
```

## Building "Complete Case" Data

Our model `fit_04` uses `wt_kg`, `age`, `sex` and `race_eth` to predict `waist`. Our identifying code is in `SEQN`.

```{r}
#| echo: true

nh_cc <- nh_H |> select(SEQN, waist, wt_kg, age, sex, race_eth) |>
  drop_na()

fit4_cc <- lm(waist ~ wt_kg + age + sex + race_eth, data = nh_cc)

n_obs(fit4_cc)
```

## "Complete Case" Results for `fit_04`

```{r}
#| echo: true
glance(fit4_cc) |> select(nobs, r.squared, adj.r.squared)

tidy(fit4_cc, conf.int = TRUE, conf.level = 0.93) |>
  select(term, estimate, std.error, conf.low, conf.high, p.value) |>
  gt() |> fmt_number(decimals = 3) |> gt_theme_guardian() 
```

## Our 4-predictor model

- Use `wt_kg`, `age`, `sex` and `race_eth` to predict `waist`.

Method | Sample | $R^2$ | `wt_kg` (93% CI)
--------: | -------: | -------: | -------------: 
Complete Cases | 4,902 | 0.878 | 0.734 (0.727, 0.742)
Training Sample | 4,000 | 0.880 | 0.735 (0.727, 0.743)
Single Imp. (all) | 5,150 | 0.877 | 0.724 (0.717, 0.731)
Multiple Imp. (25) | 5,150 | 0.879 | 0.725 (0.717, 0.733)

## Session Information {.smaller}

```{r}
#| echo: true
xfun::session_info()
```
