---
title: "431 Class 14"
author: Thomas E. Love, Ph.D.
date: "2025-10-16"
format:
  revealjs: 
    theme: dracula
    self-contained: true
    slide-number: true
    footnotes-hover: true
    preview-links: auto
    date-format: iso
    logo: 431-2025-logo-full.png
    footer: "431 Class 14 | 2025-10-16 | <https://thomaselove.github.io/431-2025/>"
---

## Today's Agenda

- Ingesting / Managing some Favorite Movies Data
- Independent Samples Comparisons with ANOVA
  - Checking the Fit
  - Transformations
- Simple Linear Regression Models
  - Fitting and Predicting with an OLS model
  - Performance of an OLS model
  - What makes a "good" fit?

## In addition to this...

See the `movies_update1.html` document (and associated `movies_update1.qmd`) found in our Shared Drive.

## Load packages and set theme

```{r}
#| echo: true
#| message: false

knitr::opts_chunk$set(comment = NA)

library(janitor)
library(naniar)
library(googlesheets4) ## to read in data from shared Google Sheet
library(rstanarm) ## to fit Bayesian linear models
library(DescTools) ## for post-hoc testing in ANOVA
library(car) ## for boxCox
library(easystats)
library(tidyverse)

theme_set(theme_minimal())

source("c14/data/Love-431.R") ## for lovedist() function
```

## Importing Data on Favorite Movies

```{r}
#| echo: true
#| message: true
gs4_deauth() # indicates to Google Drive that you're reading a public file

url_movies <- "https://docs.google.com/spreadsheets/d/17-L3FCXxMLP_07fChi6aP7721sqol7e4qx2sOKxzry4/edit?usp=sharing"  
## this is movies_2025-10-06 from our shared drive

movies_raw <- read_sheet(url_movies, na = c("", "NA")) 
```

- I am specifying that both empty cells and cells with NA indicate missing values: `read_sheet()` needs this.

```{r}
#| echo: true
dim(movies_raw)
```

## A little cleanup

```{r}
#| echo: true
#| warning: false

movies <- movies_raw |>
  select(mov_id, length, imdb_stars, metascore, mpa, 
         imdb_genres, movie) |>
  mutate(across(where(is.character), as_factor),
         movie = as.character(movie),
         mov_id = as.character(mov_id))
```

### Distinct identifiers?

```{r}
#| echo: true

nrow(movies_raw)
n_distinct(movies_raw$mov_id)
n_distinct(movies_raw$movie)
```

## Any missing values?

```{r}
#| echo: true

n_miss(movies)
miss_var_summary(movies)
```

## `mpa` is categorical

```{r}
#| echo: true
movies |> count(mpa) |> arrange(desc(n))
```

## Collapse to 3 `mpa` categories

```{r}
#| echo: true
movies <- movies |>
  mutate(mpa3 = fct_lump_n(mpa, n = 2, other_level = "Other"))

movies |> tabyl(mpa3)
```

- `fct_lump_n()` with n = 2 collapses all `mpa` values occurring less often than the top 2 `mpa` values, preserving missingness.

## `imdb_genres` is tougher to deal with

I'll make indicator variables for each of the 20 genres. A better programmer could improve this rapidly.

```{r}
#| echo: true

movies <- movies |>
  mutate(action = as.numeric(str_detect(imdb_genres, fixed("Action"))),
         adventure = as.numeric(str_detect(imdb_genres, fixed("Adventure"))),
         animation = as.numeric(str_detect(imdb_genres, fixed("Animation"))),
         biography = as.numeric(str_detect(imdb_genres, fixed("Biography"))),
         comedy = as.numeric(str_detect(imdb_genres, fixed("Comedy"))),
         crime = as.numeric(str_detect(imdb_genres, fixed("Crime"))),
         drama = as.numeric(str_detect(imdb_genres, fixed("Drama"))),
         family = as.numeric(str_detect(imdb_genres, fixed("Family"))),
         fantasy = as.numeric(str_detect(imdb_genres, fixed("Fantasy"))),
         history = as.numeric(str_detect(imdb_genres, fixed("History"))),
         horror = as.numeric(str_detect(imdb_genres, fixed("Horror"))),
         mystery = as.numeric(str_detect(imdb_genres, fixed("Mystery"))),
         music = as.numeric(str_detect(imdb_genres, fixed("Music"))),
         musical = as.numeric(str_detect(imdb_genres, fixed("Musical"))),
         romance = as.numeric(str_detect(imdb_genres, fixed("Romance"))),
         scifi = as.numeric(str_detect(imdb_genres, fixed("Sci-Fi"))),
         sport = as.numeric(str_detect(imdb_genres, fixed("Sport"))),
         thriller = as.numeric(str_detect(imdb_genres, fixed("Thriller"))),
         war = as.numeric(str_detect(imdb_genres, fixed("War"))),
         western = as.numeric(str_detect(imdb_genres, fixed("Western"))),
  )
```

## Results

```{r}
#| echo: true

movies |> select(action:war) |> colSums()
```

How many movies are categorized as both `comedy` and `drama`?

```{r}
#| echo: true
movies |> tabyl(comedy, drama)
```

## Any `action` and `musical`?

```{r}
#| echo: true

movies |> count(action, musical)
```

### Which movies?

```{r}
#| echo: true
movies |> filter(action == 1, musical == 1) |>
  select(movie, action, musical, imdb_genres, imdb_stars)
```

# Question 1

## Question 1

Do movies with different `mpa` ratings show meaningful differences in average length? We'll use **98%** confidence.

```{r}
#| echo: true
movies |> group_by(mpa3) |> reframe(lovedist(length))
```

```{r}
#| echo: true
#| output-location: slide

ggplot(movies, aes(x = mpa3, y = length)) +
  geom_violin(aes(fill = mpa3)) +
  geom_boxplot(width = 0.4, notch = TRUE) + 
  stat_summary(fun = mean, geom = "point", size = 3, col = "hotpink") +
  scale_fill_oi() +
  guides(fill = "none") +
  labs(x = "MPA rating (3 categories)", y = "Movie Length (minutes)")
```

## Second Attempt

Oops. Need to fix missingness.

```{r}
#| echo: true
#| output-location: slide

movies1 <- movies |> filter(complete.cases(mpa3, length))

ggplot(movies1, aes(x = mpa3, y = length)) +
  geom_violin(aes(fill = mpa3)) +
  geom_boxplot(width = 0.4, notch = TRUE) + 
  stat_summary(fun = mean, geom = "point", size = 3, col = "hotpink") +
  scale_fill_oi() +
  guides(fill = "none") +
  labs(x = "MPA rating (3 categories)", y = "Movie Length (minutes)")
```

What would we like to see here?

## Comparing 3 means: ANOVA

```{r}
#| echo: true

fit1 <- lm(length ~ mpa3, data = movies)
anova(fit1)
```

::: {.incremental}

- The *p* value is 0.0000008. Do we need to say more?
- How much of the variation in `length` does the `fit1` model account for?
  - proportion explained = 15409 / (15409 + 125751) = 0.109

:::

## Parameters of model `fit1`

```{r}
#| echo: true

model_parameters(fit1, ci = 0.98)
```

::: {.incremental}

- What is the regression equation here?
- `length` = 128.27 - 0.96 (if `mpa3` = R) - 17.24 (if `mpa3` = Other) 
- Can we estimate the means in each `mpa3` category?

:::


## Predicting for `mpa3` categories?

```{r}
#| echo: true

estimate_means(fit1, ci = 0.98)
```

::: {.incremental}

- How shall we compare these means and maintain overall 98% confidence?
- Remember the sample sizes: 84 movies in PG-13, 80 in R, 82 in Other.

:::

## Bonferroni comparisons?

```{r}
#| echo: true

PostHocTest(aov(fit1), method = "bonferroni", conf.level = 0.98)
```

::: {.incremental}

- What conclusions can we draw?
- Would a Tukey HSD approach be appropriate here?
  - Pre-planned comparisons? (Roughly) balanced design?

:::

## Tukey HSD comparisons

```{r}
#| echo: true

PostHocTest(aov(fit1), method = "hsd", conf.level = 0.98)
```

I like plotting these.

## Plot Tukey HSD results

```{r}
#| echo: true
par(mar=c(3,6,3,3), las = 1)
plot(PostHocTest(aov(fit1), method = "hsd", conf.level = 0.98))
```

## Check ANOVA diagnostics

```{r}
#| echo: true
#| message: false

set.seed(123)
plot(check_model(fit1, check = c("pp_check", "qq"), detrend = FALSE))
```

## Would a transformation help?

```{r}
#| echo: true

boxCox(fit1)
```

## Inverse of our outcome

```{r}
#| echo: true

movies1 <- movies1 |> mutate(invlength = 1000/length)

fit1a <- lm(invlength ~ mpa3, data = movies1)
anova(fit1a)
```

## Why did I use 1000/length?

```{r}
#| echo: true

movies1 <- movies1 |> mutate(length_inv = 1/length)

fit1b <- lm(length_inv ~ mpa3, data = movies1)
anova(fit1b)
```

## ANOVA diagnostics better?

```{r}
#| echo: true
#| message: false

set.seed(124)
plot(check_model(fit1a, check = c("pp_check", "qq"), detrend = FALSE))
```

## Estimate group means from `fit1a`

```{r}
#| echo: true

estimate_means(fit1a, ci = 0.98)
```

- What does a predicted (1000/length) of 8.11 mean?
- Back out of transformation...
  - if 1000/length = 8.11, then length = 1000/8.11 = 123.3 minutes (compare to 127.31 in untransformed data.)

## Tukey HSD for `fit1a` model

```{r}
#| echo: true
par(mar=c(3,6,3,3), las = 1)
plot(PostHocTest(aov(fit1a), method = "hsd", conf.level = 0.98))
```

## Why did the direction change?

```{r}
#| echo: true
PostHocTest(aov(fit1a), method = "hsd", conf.level = 0.98)
```

::: {.incremental}

- PG-13 and R movies still look longer than "Other"
- but a longer movie has a smaller **1000/length** value.

:::

# Question 2

## Question 2

How well can we predict `imdb_stars` (the public: 0-10 scale) using `metascore` (critics: 0-100 scale)?

```{r}
#| echo: true
#| output-location: slide
#| warning: true

ggplot(movies, aes(x = metascore, y = imdb_stars)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red", formula = y ~ x, se = TRUE) +
  geom_smooth(method = "loess", col = "blue", formula = y ~ x, se = FALSE) +
  labs(x = "Metascore from Critics", y = "Average IMDB Star Rating")
```

## Deal with missing values

```{r}
#| echo: true
#| output-location: slide

movies2 <- movies |>
  select(mov_id, metascore, imdb_stars, imdb_genres, movie) |>
  filter(complete.cases(metascore, imdb_stars))

ggplot(movies2, aes(x = metascore, y = imdb_stars)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red", formula = y ~ x, se = TRUE) +
  geom_smooth(method = "loess", col = "blue", formula = y ~ x, se = FALSE) +
  labs(x = "Metascore from Critics", y = "Average IMDB Star Rating")
```

## Which movies have low `imdb_stars`?

```{r}
#| echo: true
ggplot(movies2, aes(x = metascore, y = imdb_stars)) +
  geom_point() +
  geom_label(data = movies2 |> filter(imdb_stars < 5.5), aes(label = movie))
```

## Which three movies are those?

```{r}
#| echo: true
movies2 |> filter(imdb_stars < 5.5) |>
  select(mov_id, imdb_stars, metascore, movie, imdb_genres)
```

Let's keep these movies in, for now, at least.

## Anything else need attention?

```{r}
#| echo: true
data_codebook(movies2 |> select(metascore, imdb_stars))
```

```{r}
#| echo: true
movies2 |> reframe(lovedist(imdb_stars))
movies2 |> reframe(lovedist(metascore))
```

## Linear model, fit with OLS

Predict `imdb_stars` using `metascore` using OLS.

```{r}
#| echo: true
fit2 <- lm(imdb_stars ~ metascore, data = movies2)

## We'll use 89% confidence here, just for fun.
model_parameters(fit2, digits = 3, ci = 0.89)
```

::: {.incremental}

- What is our `fit2` model's regression equation?
- `imdb_stars` = 5.37 + 0.032 `metascore`
- Does the intercept (5.37) mean anything to us here?

:::

## Interpreting the coefficients

```{r}
#| echo: true
model_parameters(fit2, digits = 3, ci = 0.89)
```

::: {.incremental}

- If we have two movies, and movie A has a `metascore` that is 1 point higher than movie B, then ...
- our model `fit2` predicts that movie A will have an `imdb_stars` value that is 0.032 higher than movie B.
- What if movie A's metascore was 10 points higher than movie B's?

:::

## Making Predictions with `fit2`

```{r}
#| echo: true

dat_new <- tibble(metascore = c(10, 20, 30, 40, 41))
estimate_prediction(fit2, data = dat_new, ci = 0.89)
```

- Could instead use `estimate_expectation()`: same predictions, just confidence intervals rather than prediction intervals.

## Does the model perform well?

```{r}
#| echo: true
model_performance(fit2)
```

::: {.incremental}

- How can we interpret `Sigma` = 0.603?
  - About 95% of our predicted `imdb_stars` should be within $\pm 2(0.603)$ stars. Is this good?
  - `movies2` data: `imdb_stars`: range (3.6, 9.3), sd = 0.781.
  - IQR (middle half of movies) are between 7.2 and 8.1

:::

## Thinking about R-square

```{r}
#| echo: true
model_performance(fit2)
```

::: {.incremental}

- What proportion of the variation in `imdb_stars` is explained by `metascore`?
- R-square = 0.408. So what is the Pearson correlation?
- Same sign as slope: `imdb_stars` = 5.37 + 0.032 `metascore`
- Square root of R-square (0.408) is 0.639. 

:::

## Checking OLS Model Fit

Main assumptions of any simple linear regression are:

1. **linearity**: we assume that the outcome is linearly related to our predictor 
2. **constant variance** (homoscedasticity): we assume that the variation of our outcome is about the same regardless of the value of our predictor
3. **normal distribution**: we assume that the errors around the regression model at any specified values of the x-variables follow an approximately Normal distribution.

To check these assumptions, consider the following plots.

## Diagnostic Plots?

For an HTML report, run this, with 

`#| fig-height: 8` in the first line of the code chunk, then

```{r}
#| echo: true
#| eval: false

set.seed(12345)  
plot(check_model(fit2, detrend = FALSE))
```

but for the slides, I'll do...

```{r}
#| echo: true

set.seed(12345)
fit2_dx <- plot(check_model(fit2, detrend = FALSE, panel = FALSE))
```

so I can show each plots in a separate slide.

- `set.seed()` is so we all get the same posterior predictive plot.

## Posterior Predictive Check

```{r}
#| echo: true

fit2_dx[[1]]
```

## Linearity Plot

```{r}
#| echo: true

fit2_dx[[2]]
```

## Homogeneity of Variance Plot

```{r}
#| echo: true

fit2_dx[[3]]
```

## Influential Observations

```{r}
#| echo: true

fit2_dx[[4]]
```

## What is point 228?

```{r}
#| echo: true

movies2 |> slice(228) |>
  select(mov_id, metascore, imdb_stars, movie)
```

- If we removed "The Room", we would see some changes in our model.
- "The Room" is the movie with the lowest `metascore`, and the lowest `imdb_stars` of any of our movies.

## Normality of Residuals

```{r}
#| echo: true

fit2_dx[[5]]
```

## Which movies are poorly fit?

```{r}
#| echo: true

movies2 <- movies2 |> mutate(residf2 = resid(fit2), fitf2 = fitted(fit2))
ggplot(movies2, aes(x = residf2)) +
  geom_histogram(bins = 25, fill = "navy", col = "white")
```

## Which movies miss the mark?

Which movies are more than 1.2 stars off in their predictions?

```{r}
#| echo: true

movies2 |> filter(residf2 < -1.2 | residf2 > 1.2) |>
  select(mov_id, metascore, imdb_stars, movie, residf2, fitf2) |>
  arrange(residf2)
```

## Regression Model Calibration?

```{r}
#| echo: true

ggplot(movies2, aes(x = imdb_stars, y = fitf2)) +
  geom_text(aes(label = mov_id)) +
  geom_abline( slope = 1, intercept = 0 , col = "sienna", lwd = 2)
```

## Calibration of this Model?

```{r}
#| echo: true

ggplot(movies2, aes(x = imdb_stars, y = fitf2)) +
  geom_point() +
  geom_label(data = movies2 |> filter(imdb_stars < 5.4), aes(label = movie)) +
  geom_abline( slope = 1, intercept = 0 , col = "sienna", lwd = 2)
```

## What if we dropped the three outliers?

We'd have to have a real reason to do this, of course. It couldn't just be "our model doesn't fit them well."

```{r}
#| echo: true

movies2a <- movies2 |> filter(imdb_stars >= 5.5)

dim(movies2)
dim(movies2a)
```

## Scatterplot with and without

What happens when we drop our three "outliers"?

```{r}
#| echo: true
#| output-location: slide

p1 <- ggplot(movies2, aes(x = metascore, y = imdb_stars)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red", formula = y ~ x, se = TRUE) +
  geom_smooth(method = "loess", col = "blue", formula = y ~ x, se = FALSE) +
  labs(x = "Metascore from Critics", y = "Average IMDB Star Rating", 
       title = "245 Movies")

p2 <- ggplot(movies2a, aes(x = metascore, y = imdb_stars)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red", formula = y ~ x, se = TRUE) +
  geom_smooth(method = "loess", col = "blue", formula = y ~ x, se = FALSE) +
  labs(x = "Metascore from Critics", y = "Average IMDB Star Rating", 
       title = "242 Movies")

p1 + p2
```

## With and without 3 movies

```{r}
#| echo: true
## with Madea Goes to Jail, Doom, and The Room
model_parameters(fit2, ci = 0.89)


## without those movies
fit2a <- lm(imdb_stars ~ metascore, data = movies2a)
model_parameters(fit2a, ci = 0.89)
```

## With and without 3 movies

Summaries aren't directly comparable, since we've dropped three movies.

```{r}
#| echo: true
## with Madea Goes to Jail, Doom, and The Room
model_performance(fit2, ci = 0.89)

## without those movies
model_performance(fit2a, ci = 0.89)
```

## Prediction if `metascore` is 60

```{r}
#| echo: true

dat_new2 <- tibble(metascore = 60)

## with Madea Goes to Jail, Doom, and The Room
estimate_expectation(fit2, ci = 0.89, data = dat_new2)

## without those movies
estimate_expectation(fit2a, ci = 0.89, data = dat_new2)
```

## Are the diagnostic plots better?

```{r}
#| echo: true

set.seed(12121)
fit2a_dx <- plot(check_model(fit2a, detrend = FALSE, panel = FALSE))
```

## "With" on left, "Without" on right

```{r}
#| echo: true

p1 <- fit2_dx[[1]]
p2 <- fit2a_dx[[1]]
p1 + p2
```

## "With" on left, "Without" on right

```{r}
#| echo: true

p1 <- fit2_dx[[2]]
p2 <- fit2a_dx[[2]]
p1 + p2
```

## "With" on left, "Without" on right

```{r}
#| echo: true

p1 <- fit2_dx[[3]]
p2 <- fit2a_dx[[3]]
p1 + p2
```

## "With" on left, "Without" on right

```{r}
#| echo: true

p1 <- fit2_dx[[4]]
p2 <- fit2a_dx[[4]]
p1 + p2
```

## "With" on left, "Without" on right

```{r}
#| echo: true

p1 <- fit2_dx[[5]]
p2 <- fit2a_dx[[5]]
p1 + p2
```

## GOOD LUCK ON THE QUIZ!

```{r}
#| echo: true
xfun::session_info()
```
